---
title: "AQ Bench AOA Comparison"
author: "Marvin Ludwig"
date: "26/07/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(caret)
library(RStoolbox)
library(mlutils)
library(viridis)
library(raster)
library(ggpubr)

```

# All Predictors, CV-Juelich


## Model Infos

```{r}
model = readRDS("data/models/model_allvars_juelichcv.RDS")
model
```

## Variable Importance (Gini)

```{r}
plot(varImp(model, scale = FALSE))
```

## Validation on Test Set

```{r}
testdata = readRDS("data/validations/validation_allvars_juelichcv.RDS")

r = round(Metrics::rmse(testdata$o3_average_values, testdata$pred_o3_average_values), 2)


ggplot(testdata, aes(x = o3_average_values, y = pred_o3_average_values))+
    geom_point()+
    scale_x_continuous(name = expression(paste("Observed ",O[3] ," Average Values")), limits = c(0, 60), expand = c(0,0))+
    scale_y_continuous(name = expression(paste("Predicted ",O[3] ," Average Values")), limits = c(0, 60), expand = c(0,0))+
    geom_abline(slope = 1, intercept = 0, color = "red")+
    stat_regline_equation(aes(label = ..rr.label..), label.x = 1)+
    annotate(geom = "text", label = paste0("RMSE = ", r), x = 1, y = 50, hjust = 0)+
    coord_equal()+
    theme_bw()
```






## AOA Stats

```{r}
a = readRDS("data/aoas/aoa_allvars_juelichcv.RDS")
aoa_stats = attributes(a)$aoa_stats

print(paste0("Mean Distance in Training Data: ", round(aoa_stats$Mean_train, 2)))


print(paste0("DI threshold: ", round(aoa_stats$threshold, 4)))



```

```{r}

p = raster("data/predictions/prediction_allvars_juelichcv.grd")

a2 = a[[2]]
a2[a2 == 1] = NA


pmap = ggR(p, geom_raster = TRUE)+
    scale_fill_gradientn(name = expression(paste(O[3] ," Average Values")),
                         colors = viridis(50), limits = c(15, 50))+
    ggnewscale::new_scale_fill()+
    ggR(a2, ggLayer = TRUE, forceCat = TRUE, geom_raster = TRUE, alpha = NA)+
    scale_fill_manual(name = "Out of AOA", values = c("0" = "grey70"), na.value = "transparent")+
    coord_equal(expand = FALSE)+
    theme_map()


pmap

```

## Standard Deviation of Predictions

```{r}
p = raster("data/predictionSDs/sd_allvars_juelichcv.grd")

a2 = a[[2]]
a2[a2 == 1] = NA


pmap = ggR(p, geom_raster = TRUE)+
    scale_fill_gradientn(name = expression(paste(O[3] ," Average Values SD[%]")),
                         colors = viridis(50), limits = c(0, 70))+
    coord_equal(expand = FALSE)+
    theme_map()


pmap

```


```{r}
a = raster::stack(p, a[[2]])
a = as.data.frame(a)

a$AOA = as.factor(a$AOA)
ggplot(a, aes(y = layer, x = AOA, group = AOA))+
    geom_boxplot()+
    scale_y_continuous(name = expression(paste(O[3] ," Average Values SD[%]")))+
    theme_pubr()
```




# Forward Feature Selection, Juelich CV



## Model Infos

```{r}
model = readRDS("data/models/model_ffs_juelichcv.RDS")
model
```





## Variable Importance (Gini)

```{r}
plot(varImp(model, scale = FALSE))
```

## Validation on Test Set

```{r}
testdata = readRDS("data/validations/validation_ffs_juelichcv.RDS")

r = round(Metrics::rmse(testdata$o3_average_values, testdata$pred_o3_average_values), 2)


ggplot(testdata, aes(x = o3_average_values, y = pred_o3_average_values))+
    geom_point()+
    scale_x_continuous(name = expression(paste("Observed ",O[3] ," Average Values")), limits = c(0, 60), expand = c(0,0))+
    scale_y_continuous(name = expression(paste("Predicted ",O[3] ," Average Values")), limits = c(0, 60), expand = c(0,0))+
    geom_abline(slope = 1, intercept = 0, color = "red")+
    stat_regline_equation(aes(label = ..rr.label..), label.x = 1)+
    annotate(geom = "text", label = paste0("RMSE = ", r), x = 1, y = 50, hjust = 0)+
    coord_equal()+
    theme_bw()
```



## AOA Stats

```{r}
a = readRDS("data/aoas/aoa_ffs_juelich_old.RDS")
aoa_stats = attributes(a)$aoa_stats

print(paste0("Mean Distance in Training Data: ", round(aoa_stats$Mean_train, 2)))


print(paste0("DI threshold: ", round(aoa_stats$threshold, 4)))

```

```{r}

p = raster("data/predictions/prediction_ffs_juelichcv.grd")
mlutils::ggAOA(p, a$AOA)

```


## Standard Deviation of Predictions

```{r}
p = raster("data/predictionSDs/sd_ffs_juelichcv.grd")

a2 = a[[2]]
a2[a2 == 1] = NA


pmap = ggR(p, geom_raster = TRUE)+
    scale_fill_gradientn(name = expression(paste(O[3] ," Average Values SD[%]")),
                         colors = viridis(50), limits = c(0, 70))+
    coord_equal(expand = FALSE)+
    theme_map()


pmap

```


```{r}
a = raster::stack(p, a[[2]])
a = as.data.frame(a)

a$AOA = as.factor(a$AOA)
ggplot(a, aes(y = climatic_zone, x = AOA, group = AOA))+
    geom_boxplot()+
    scale_y_continuous(name = expression(paste(O[3] ," Average Values SD[%]")))+
    theme_pubr()
```


# No Latitude and Climatic Zone, Juelich-CV


## Model Infos

```{r}
model = readRDS("data/models/model_nolat_juelichcv.RDS")
model
```

## Variable Importance (Gini)

```{r}
plot(varImp(model, scale = FALSE))
```

## Validation on Test Set

```{r}
testdata = readRDS("data/validations/validation_nolat_juelichcv.RDS")

r = round(Metrics::rmse(testdata$o3_average_values, testdata$pred_o3_average_values), 2)


ggplot(testdata, aes(x = o3_average_values, y = pred_o3_average_values))+
    geom_point()+
    scale_x_continuous(name = expression(paste("Observed ",O[3] ," Average Values")), limits = c(0, 60), expand = c(0,0))+
    scale_y_continuous(name = expression(paste("Predicted ",O[3] ," Average Values")), limits = c(0, 60), expand = c(0,0))+
    geom_abline(slope = 1, intercept = 0, color = "red")+
    stat_regline_equation(aes(label = ..rr.label..), label.x = 1)+
    annotate(geom = "text", label = paste0("RMSE = ", r), x = 1, y = 50, hjust = 0)+
    coord_equal()+
    theme_bw()
```

## AOA Stats

```{r}
a = readRDS("data/aoas/aoa_nolat_juelichcv.RDS")
aoa_stats = attributes(a)$aoa_stats

print(paste0("Mean Distance in Training Data: ", round(aoa_stats$Mean_train, 2)))
print(paste0("DI threshold: ", round(aoa_stats$threshold, 4)))
```


```{r}
p = raster("data/predictions/prediction_nolat_juelichcv.grd")
mlutils::ggAOA(p, a$AOA)
```

## Standard Deviation of Predictions
```{r}
p = raster("data/predictionSDs/sd_nolat_juelichcv.grd")

a2 = a[[2]]
a2[a2 == 1] = NA


pmap = ggR(p, geom_raster = TRUE)+
    scale_fill_gradientn(name = expression(paste(O[3] ," Average Values SD[%]")),
                         colors = viridis(50), limits = c(0, 70))+
    coord_equal(expand = FALSE)+
    theme_map()


pmap

```

```{r}
a = raster::stack(p, a[[2]])
a = as.data.frame(a)

a$AOA = as.factor(a$AOA)
ggplot(a, aes(y = climatic_zone, x = AOA, group = AOA))+
    geom_boxplot()+
    scale_y_continuous(name = expression(paste(O[3] ," Average Values SD[%]")))+
    theme_pubr()
```

# FFS, No Latitude and Climatic Zone, Juelich-CV


## Model Infos

```{r}
model = readRDS("data/models/model_ffsnolat_juelichcv.RDS")
model
```

## Variable Importance (Gini)

```{r}
plot(varImp(model, scale = FALSE))
```

## Validation on Test Set

```{r}
testdata = readRDS("data/validations/validation_ffsnolat_juelichcv.RDS")

r = round(Metrics::rmse(testdata$o3_average_values, testdata$pred_o3_average_values), 2)


ggplot(testdata, aes(x = o3_average_values, y = pred_o3_average_values))+
    geom_point()+
    scale_x_continuous(name = expression(paste("Observed ",O[3] ," Average Values")), limits = c(0, 60), expand = c(0,0))+
    scale_y_continuous(name = expression(paste("Predicted ",O[3] ," Average Values")), limits = c(0, 60), expand = c(0,0))+
    geom_abline(slope = 1, intercept = 0, color = "red")+
    stat_regline_equation(aes(label = ..rr.label..), label.x = 1)+
    annotate(geom = "text", label = paste0("RMSE = ", r), x = 1, y = 50, hjust = 0)+
    coord_equal()+
    theme_bw()
```

## AOA Stats

```{r}
a = readRDS("data/aoas/aoa_ffsnolat_juelichcv.RDS")
aoa_stats = attributes(a)$aoa_stats

print(paste0("Mean Distance in Training Data: ", round(aoa_stats$Mean_train, 2)))
print(paste0("DI threshold: ", round(aoa_stats$threshold, 4)))
```


```{r}
p = raster("data/predictions/prediction_ffsnolat_juelichcv.grd")
mlutils::ggAOA(p, a$AOA)
```

## Standard Deviation of Predictions


```{r}
p = raster("data/predictionSDs/sd_ffsnolat_juelichcv.grd")

a2 = a[[2]]
a2[a2 == 1] = NA


pmap = ggR(p, geom_raster = TRUE)+
    scale_fill_gradientn(name = expression(paste(O[3] ," Average Values SD[%]")),
                         colors = viridis(50), limits = c(0, 70))+
    coord_equal(expand = FALSE)+
    theme_map()


pmap

```

```{r}
a = raster::stack(p, a[[2]])
a = as.data.frame(a)

a$AOA = as.factor(a$AOA)
ggplot(a, aes(y = climatic_zone, x = AOA, group = AOA))+
    geom_boxplot()+
    scale_y_continuous(name = expression(paste(O[3] ," Average Values SD[%]")))+
    theme_pubr()
```